---
title: "Random walk"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(gganimate)
library(magick)
library(proxy)

my_theme = theme_light() + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
```

## Step 0: Coefficient selection

```{r}
# N: Total number of points
# R: A vector of radius
# P: A vector of the proportion of points in each ring area
# Time: The number of days (running times)
# pc: Probability of being infected
# pr: Probability of being attracted by the restaurant
# transform_probability: A data frame contains the probability of symptom changes
# min_infection_range: A number indicates the minimum range of infection
# speed: A vector of movement speed of points with different symptoms
# Num_public: A number indicates the number of public places
# Hospital_capacity: A decimal indicates the ratio of hospital capacity
# vacstart: A number of the start day of vaccine
# social_distance: A number of social distance
# Quarantine_ratio: A number of the ratio of quarantine
# n_city: A number indicates the number of city

N = 3000
# R need to be decreasing
R = c(40,30,20,10)
# P should be the value corresponding to R
P = c(1,2,3,4)
Times = 60
pc = 0.1
pr = 0.4
transform_probability = data.frame(ease = c(0.2,0.2,0.1), worsen = c(0.2,0.2,0.4))
rownames(transform_probability) = 3:5
min_infection_range = 1e-2
speed = c(1, 1, 0.8, 0.3, 0.1, 0, 1)
Num_public = 20
Hospital_capacity = 0.01
vacstart = 12
social_distance = 0.6  
Quarantine_ratio = 0.6
n_city = 2
```

```{r}
calculate_alpha = function(N, R, P, c){
  # N: Total number of points
  # R: A vector of radius
  # P: A vector of the proportion of points in each ring area
  # c: Correction coefficient
  
  L = length(R)
  population = P/sum(P)*N
  S = R^2
  area = S - c(S[2:L],0)
  density = population/area
  ratio = density / c(0, density[1:(L-1)])
  alpha = 1/ratio*c
  
  return(alpha)
}
```

```{r}
# alpha: A vector of probability of being able to get out of the wall

# alpha should be the value corresponding to R
# This 1.25 is calculate by whole_data when only calculate step 1 to 4
# To let the number of points in each ring after 300 runnings is still the same 
alpha = calculate_alpha(N, R, P, 1.25)
```

## Step 1: Intialize points

```{r}
random_point_circle = function(R, N, x_center = 0, y_center = 0){
  # R: Radiu
  # N: Number of points
  
  if(length(R) != 1)
    stop('Length of R is not 1 in random_point_circle!')
  if(length(N) != 1)
    stop('Length of N is not 1 in random_point_circle!')
  if(N == 0)
    return(data.frame(X = NULL, Y = NULL))
  
  U = runif(N, 0, R^2)
  A = runif(N, 0 ,2*pi)
  X = sqrt(U)*cos(A) + x_center
  Y = sqrt(U)*sin(A) + y_center
  return(data.frame(X = X, Y = Y))
}
```

```{r}
intialize_points = function(N, R, P, x_center = 0, y_center = 0){
  # N: Total number of points
  # R: A vector of radius
  # P: A vector of the proportion of points in each ring area
  
  if(length(N) != 1)
    stop('Length of N is not 1 in intialize_points!')
  if(length(R) != length(P))
    stop('R and P have different length in intialize_points!')
  if(length(R) == 0)
    stop('Length of R is 0 in intialize_points!')
  
  L = length(R)
  S = R^2
  
  S = S/sum(S)
  P = P/sum(P)
  
  if(mean(P/S == sort(P/S)) != 1)
    stop('The proportion of area is not increasing in intialize_points!')
  
  data = data.frame(X = NULL, Y = NULL)
  
  number_of_points = rep(0, L)
  for(i in 1:L){
    total_area = S[i]
    if(i == L){
      current_area = S[i]
    } else{
      current_area = S[i]-S[i+1]
    }
    need_points = P[i]*N - number_of_points[i]
    generate_points = round(need_points / current_area * total_area)
    data = rbind(data, random_point_circle(R[i],  generate_points, x_center, y_center))
    if(i == L){
      number_of_points[L] = number_of_points[L] + generate_points 
    } else{
      number_of_points[i:L] = number_of_points[i:L] + round((S[i:L] - c(S[(i+1):L],0)) / total_area * generate_points)
    }

  }
  if(nrow(data)<N)
    data = rbind(data, random_point_circle(R[1], N-nrow(data), x_center, y_center))
  else
    data = data[1:N,]
  
  return(list(data, number_of_points))
}
```

```{r}
intialize = intialize_points(N, R, P,20,20)
data = intialize[[1]]
# To check if the number of data is right
number_of_points = intialize[[2]]
number_of_points
P/sum(P)*N
```

```{r}
# To check the number of data in each ring
check_data = data %>% mutate(Radiu = sqrt(X^2+Y^2))
check_data %>% filter(Radiu<R[1]) %>% nrow()
check_data %>% filter(Radiu<R[2]) %>% nrow()
check_data %>% filter(Radiu<R[3]) %>% nrow()
check_data %>% filter(Radiu<R[4]) %>% nrow()
```

### Step2: Plot points in ggplot

```{r}
plot_points = function(data, condition){
  # data: A data frame contains X and Y in first 2 column
  # condition: A vector contains 7 factors of illness
  
  c = colnames(data)
  if(c[1] != 'X' | c[2] != 'Y')
    stop('Wrong name in data in plot_points!')
  
  if(nrow(data) != length(condition %>% unlist))
    stop('Wrong nrow of condition in plot_points!')
  
  t = tibble(X = data$X, Y = data$Y, condition = factor(condition, levels = 1:7))
  g = t %>%
    ggplot(aes(x = X, y = Y, color = condition)) + 
    geom_point(size = 0.1, alpha = 0.6) + 
    scale_color_manual(values = c('#00CC00', '#FFCC00', '#FF69B4', '#DC143C', '#8B0000', '#000000', '#00CCFF'), labels = c('Healthy', 'Incubation', 'Moderate', 'Severe', 'Cirtical', 'Death', 'Cure'), name = 'Condition') + 
    coord_fixed() + 
    my_theme
  g
}
```

```{r}
# Condition meaning and color
# 1: Healthy, '#00CC00', Electric Green
# 2: Incubation period, '#FFCC00', Tangerine Yellow
# 3: Moderate, '#FF69B4', Hot Pink
# 4: Severe, '#DC143C', Crimson
# 5: Cirtical, '#8B0000', Dark Red
# 6: Death, '#000000', Black
# 7: Cure, '#00CCFF', Deep Sky Blue

test_condition = sample(1:7, N, replace = TRUE) 
plot_points(data, test_condition)
```

## Step 3: Random walk for one time

```{r}
random_walk = function(data, v){
  # data: A data frame contains X and Y in first 2 column
  # v: A vector contains the speed of points
  
  N0 = nrow(data)
  if(N0 != length(v %>% unlist))
    stop('Wrong nrow of v in Random_Walk!')
  
  distance = rnorm(N0, v, sd = v/1.5)
  distance[distance < 0] = 0
  
  A = runif(N0, 0 ,2*pi)
  data$X = data$X + distance * cos(A)
  data$Y = data$Y + distance * sin(A)
  
  return(data)
}
```

```{r}
v = rnorm(N, 1, 0.5)
v[v < 0] = 0
new_data = random_walk(data, v)
plot_points(new_data, test_condition)
```

## Step 4: Build the wall

```{r}
through_wall = function(last_data, new_data, R, alpha, x_center = 0, y_center = 0){
  # last_data: A data frame contains X and Y which is last position
  # new_data: A data frame contains X and Y which is new position
  # R: A vector of radius
  # alpha: A vector of probability of being able to get out of the wall
  
  last_R = sqrt((last_data$X-x_center)^2 + (last_data$Y-y_center)^2)
  new_R = sqrt((new_data$X-x_center)^2 + (new_data$Y-y_center)^2)
  
  R0 = c(Inf, R, 0)
  last_R0 = cut(last_R, breaks = R0, labels = (length(R)+1):1) %>% as.numeric()
  new_R0 = cut(new_R, breaks = R0, labels = (length(R)+1):1) %>% as.numeric()
  
  # wall_level: for example, R = c(40,30,20,10)
  # 1. R<10
  # 2. 10<R<20
  # 3. 20<R<30
  # 4. 30<R<40
  # 5. R>40
  
  index = which(last_R0 < new_R0)
  wall_level = last_R0[index]
  
  # To make sure alpha[1] is the wall_level 1's probability
  alpha0 = rev(alpha)
  alpha_all = alpha0[wall_level]
  
  U = runif(length(index), 0 ,1)
  
  index_run = which(U > alpha_all)
  wall_level_run = wall_level[index_run]
  index_run = index[index_run]
  
  distance = new_data[index_run,c('X', 'Y')] - last_data[index_run,c('X', 'Y')]
  distance = sqrt(distance$X^2 + distance$Y^2)
  
  R1 = last_R[index_run]
  R2 = new_R[index_run]
  rest_distance = distance/(R1+R2)*R2
  
  ratio = (1-2*rest_distance/new_R[index_run])
  ratio = ifelse(ratio < -0.5, -0.5, ratio)
  
  length_run = length(index_run)
  center = data.frame(X = rep(x_center, length_run), Y = rep(y_center, length_run))
  new_data[index_run,] = (new_data[index_run,]-center) * ratio + center
  
  return(new_data)
}
```

## Step 5: Infection

```{r}
initialize_infector = function(condition, n){
  # condition: A vector contains 7 factors of illness and its duration
  # n : Number of infectors in first day
  
  index = sample(1:nrow(condition), n, replace = FALSE)
  condition[index, 1] = 2
  
  return(condition)
}
```

```{r}
pairwise_dist = function(data1, data2){
  # data1: A data frame contains X and Y which is the position
  # data2: A data frame contains X and Y which is the position
  
  Dist_matrix = as.matrix(proxy::dist(data1, data2))
  
  return(Dist_matrix)
}
```

```{r}
infection = function(data, v, condition, infectious_ability, protection_ability, pc, trigger_social_distance = FALSE , sd = social_distance){
  # data: A data frame contains X and Y which is the position
  # v: A vector contains the speed of points
  # condition: A vector contains 7 factors of illness and its duration

  incubation_infection = ifelse(condition$duration > 3, 1, 0)
  incubation_index = which(condition$condition == 2)
  
  # Condition infection speed
  # 1: Healthy, 0
  # 2: Incubation period, 1 if duration > 3, 0 else
  # 3: Moderate, 1
  # 4: Severe, 1.5
  # 5: Cirtical, 2
  # 6: Death, 0
  # 7: Cure, 0
  
  infection_speed = sapply(condition$condition, function(x) switch(x, '1' = 0,'2' = 1, '3' = 1, '4' = 1.5, '5' = 2, '6' = 0, '7' =  0))
  infection_speed[incubation_index] = infection_speed[incubation_index] * incubation_infection[incubation_index]
  
  infection_index = which(infection_speed > 0)
  infection_length = length(infection_index)
  canbe_infected_index = which(condition$condition == 1)
  canbe_infected_length = length(canbe_infected_index)
  
  if(infection_length == 0)
    return(condition)
  
  distance = pairwise_dist(data[infection_index,], data[canbe_infected_index,])
  
  # Step 13 zzq
  # social_distance
  U = runif(nrow(distance)*ncol(distance), 0.5, 1)
  U = matrix(U, nr = nrow(distance), nc = ncol(distance))
  if(trigger_social_distance)
    distance = distance + sd*U

  
  infection_change = function(condition2,infectious_ability2, protection_ability2, pc, infection_radius){
    
    infection_radius = v[infection_index] * infection_speed[infection_index] * infectious_ability2[infection_index] * protection_ability2[infection_index] * infection_radius + min_infection_range
    infection_radius = matrix(rep(infection_radius, canbe_infected_length), nr = infection_length)
    
    possible_infection = which(distance<infection_radius, arr.ind = TRUE)
    possible_infection = possible_infection[,2] %>% unique()
  
    U = runif(length(possible_infection), 0, 1)
  
    protect_value = protection_ability2[colnames(distance)[possible_infection] %>% as.numeric()]
    confirmed_infection = possible_infection[U < pc * protect_value]
    confirmed_infection = colnames(distance)[confirmed_infection] %>% as.numeric()
    
    condition2[confirmed_infection, 'condition'] = 2
    condition2[confirmed_infection, 'duration'] = 0
    
    return(condition2)
  }
  
  condition = infection_change(condition, infectious_ability, protection_ability, pc, 1)
  condition = infection_change(condition, infectious_ability, protection_ability, pc/4, 2)
  
  return(condition)
}
```

## Step 6: Condition worsens or eases

```{r}
symptom_change = function(condition, v, new_condition, new_v, now, ease, worsen, nochange_day = 3){
  index = which(condition$condition == now & condition$duration > nochange_day)
  l = length(index)
  
  U = runif(l, 0 ,1)
  ease_index = index[U < transform_probability[as.character(now),1]]
  worsen_index = index[U > 1-transform_probability[as.character(now),2]]
    
  new_condition[ease_index, 'condition'] = ease
  new_condition[ease_index, 'duration'] = 0
  new_condition[worsen_index, 'condition'] = worsen
  new_condition[worsen_index, 'duration'] = 0
  new_v[ease_index] = v[ease_index] * speed[ease]/speed[now]
  new_v[worsen_index] = v[worsen_index] * speed[worsen]/speed[now]
    
  return(list(new_condition, new_v))
}
```

```{r}
condition_change = function(condition, v, transform_probability, speed){
  # condition: A vector contains 7 factors of illness and its duration
  # v: A vector contains the speed of points
  # transform_probability: A data frame contains the probability of symptom changes
  # speed: A vector of movement speed of points with different symptoms
  
  new_condition = condition
  new_v = v
  
  # End of incubation period, condition 2->3
  incubation_index = which(condition$condition == 2)
  incubation_length = length(incubation_index)
  
  U = rnorm(incubation_length, 7, 2)
  symptom_date = ifelse(U < 3 ,3, U)
  symptom_index = incubation_index[condition$duration[incubation_index] > symptom_date]
  
  new_condition[symptom_index, 'condition'] = 3
  new_condition[symptom_index, 'duration'] = 0
  new_v[symptom_index] = v[symptom_index] * speed[3]/speed[2]
  
  # End of a symptom period, condition 3,4,5 -> (7,4) (3,5) (4,6)
  temp = symptom_change(condition, v, new_condition, new_v, 3, 7, 4)
  new_condition = temp[[1]]
  new_v = temp[[2]]
  
  temp = symptom_change(condition, v, new_condition, new_v, 4, 3, 5)
  new_condition = temp[[1]]
  new_v = temp[[2]]
  
  temp = symptom_change(condition, v, new_condition, new_v, 5, 4, 6)
  new_condition = temp[[1]]
  new_v = temp[[2]]
  
  return(list(new_condition, new_v))
}
```

## Step 7: Intialize public place

```{r}
random_public_place = function(R, class, capacity, x_center = 0, y_center = 0){
  # R: Radiu
  # class: A number indicates the category of public_place
  # capacity: A number indicates the number of maximum points in this place
  
  if(length(R) != 1)
    stop('Length of R is not 1 in random_public_place!')
  if(!class %in% 1:4)
    stop('Class is not right in random_public_place!')
  if(capacity <= 0)
    stop('Capacity is not right in random_public_place!')
  
  # class:
  # 1: Hospital, To increase the probability of healing
  # 2: Train Station: To let people leave and come
  # 3: Restaurant/School/Supermarket: Crowded locations
  # 4：Hotel: To quarantine close contacts
  
  A = runif(1, 0 ,2*pi)
  X = R*cos(A) + x_center
  Y = R*sin(A) + y_center
  return(data.frame(X = X, Y = Y, Class = class, Capacity = capacity))
}
```

```{r}
intialize_public_place = function(R, P, N, Num_public, Hospital_capacity, x_center = 0, y_center = 0){
  # N: Total number of points
  # R: A vector of radius
  # P: A vector of the proportion of points in each ring area
  # Num_public: A number indicates the number of public places
  # Hospital_capacity: A decimal indicates the ratio of hospital capacity
  
  if(Num_public < 2)
    stop('The number of public place is too less in intialize_public_place!')
  if(Hospital_capacity > 1 | Hospital_capacity < 0)
    stop('The capacity of hospital is wrong in intialize_public_place!')
  
  data_public = data.frame(X = NULL, Y = NULL, Class = NULL, Capacity = NULL)
  
  L = length(R)
  population = P/sum(P)*N
  S = R^2
  area = S - c(S[2:L],0)
  density = population/area
  density = density/sum(density)
  density_cumsum = c(0, cumsum(density))
  
  U = runif(1, 0, 1)
  data_station = random_public_place((R[L-2] - R[L])*U + R[L], 2, N/100, x_center, y_center)
  data_public = rbind(data_public, data_station)
  
  num_hospital = ceiling((Num_public-1)/6)
  num_hotel = round((Num_public-1)/3)
  num_school = Num_public - 1 - num_hospital - num_hotel
  
  build_public = function(class2, capacity2, num2){
    
    data_public2 = data.frame(X = NULL, Y = NULL, Class = NULL, Capacity = NULL)
    
    capacity_num = capacity2/num2
    capacity_num = rnorm(num2, capacity_num, capacity_num/3)
    capacity_num[capacity_num<1] = 1
    capacity_num = round(capacity_num)
    
    U = runif(num2, 0 ,1)
    pos = sapply(U, function(x) mean(x>density_cumsum)*(L+1))
    
    U = runif(num2, 0 ,1)
    for(i in 1:num2){
      R0 = c(R, 0)
      R_i = (R0[pos[i]] - R0[pos[i]+1])*U[i] + R0[pos[i]+1]
      data_place = random_public_place(R_i, class2, capacity_num[i], x_center, y_center)
      data_public2 = rbind(data_public2, data_place)
    }
    return(data_public2)
  }
  
  data_hospital = build_public(1, N*Hospital_capacity, num_hospital)
  data_school = build_public(3, N*Hospital_capacity*10, num_school)
  data_hotel = build_public(4, N*Hospital_capacity*3, num_hotel)
  
  data_public = rbind(data_public, data_hospital)
  data_public = rbind(data_public, data_school)
  data_public = rbind(data_public, data_hotel)
  
  data_public = cbind(data_public, Current = 0, Index = 1:nrow(data_public))
  
  return(data_public)
}
```

```{r}
plot_points = function(data, condition, data_public){
  # data: A data frame contains X and Y in first 2 column
  # condition: A vector contains 7 factors of illness and its duration
  # data_public: A data frame contains X, Y, class and condition.
  
  c = colnames(data)
  if(c[1] != 'X' | c[2] != 'Y')
    stop('Wrong name in data in plot_points!')
  
  if(nrow(data) != length(condition %>% unlist))
    stop('Wrong nrow of condition in plot_points!')
  
  data_public$Class = factor(data_public$Class, levels = 1:4, labels = c('Hospital', 'Station', 'Restaurant', 'Hotel'))
  
  t = tibble(X = data$X, Y = data$Y, condition = factor(condition, levels = 1:7))
  g = t %>%
    ggplot(aes(x = X, y = Y, color = condition)) + 
    geom_point(size = 0.1, alpha = 0.6) + 
    geom_point(data = data_public, aes(x = X, y = Y, size = log(Capacity), color = Class), alpha = 0.8) + 
    scale_color_manual(values = c('1' = '#00CC00', '2' = '#FFCC00', '3' = '#FF69B4', '4' = '#DC143C', '5' = '#8B0000', '6' = '#000000', '7' = '#00CCFF', 'Hospital' = '#FF0000', 'Station' = '#FF6600', 'Restaurant' = '#7FFFD4', 'Hotel' = '#CC99CC'), labels = c('Healthy', 'Incubation', 'Moderate', 'Severe', 'Cirtical', 'Death', 'Cure', 'Hospital', 'Station', 'Restaurant', 'Hotel'), name = 'Condition') +
    scale_size(range = c(2,3.5), name = 'Capacity', guide = FALSE) + 
    coord_fixed() + 
    my_theme
  g
}
```

```{r}
# Condition meaning and color
# 1: Healthy, '#00CC00', Electric Green
# 2: Incubation period, '#FFCC00', Tangerine Yellow
# 3: Moderate, '#FF69B4', Hot Pink
# 4: Severe, '#DC143C', Crimson
# 5: Cirtical, '#8B0000', Dark Red
# 6: Death, '#000000', Black
# 7: Cure, '#00CCFF', Deep Sky Blue
# Hospital, '#FF0000', Red
# Station, '#FF6600', Safety Orange
# Restaurant, '#7FFFD4', Aquamarine
# Hotel, '#CC99CC', Lilac

data_public = intialize_public_place(R, P, N, Num_public,Hospital_capacity, 20, 20)
plot_points(data, test_condition, data_public)
```

## Step 8: Move to public areas

```{r}
moveto_restaurant = function(last_data, new_data, data_public, people_duration, before_place_info, v, condition){
  # last_data: A data frame contains X and Y which is last position
  # new_data: A data frame contains X and Y which is new position
  # data_public: A data frame contains X, Y, class and condition.
  # people_duration: A data frame contains each points' place and duration
  # before_place_info: A data frame contains info of points before move to place.
  # v: A vector contains the speed of points
  # condition: A vector contains 7 factors of illness and its duration
  
  data_public2 = data_public %>% filter(Class == 3)
  
  n_public = nrow(data_public2)
  N = nrow(last_data)
  
  distance = pairwise_dist(last_data, data_public2[,c('X', 'Y')])
  
  influence_dist = matrix(rep(v*3, n_public), nc = n_public)
  influence_index = which(distance<influence_dist, arr.ind = TRUE)
  
  possible_index = which(people_duration$place == 0 & people_duration$duration > 4)
  influence_index = influence_index[influence_index[, 1] %in% possible_index,]
  influence_index = matrix(influence_index, nc = 2)
  
  if(nrow(influence_index) == 0)
    return(list(new_data, before_place_info, v, data_public, people_duration))
  
  U = runif(nrow(influence_index), 0, 1)
  
  confirmed_index = influence_index[U < pr,]
  confirmed_index = matrix(influence_index, nc = 2)
  if(nrow(confirmed_index) == 0)
    return(list(new_data, before_place_info, v, data_public, people_duration))
  
  notdupli = !duplicated(confirmed_index[,1])
  cr = confirmed_index[notdupli,1]
  cc = confirmed_index[notdupli,2]
  
  rest_capacity = data_public2[unique(cc),]$Capacity - data_public2[unique(cc),]$Current
  need_capacity = table(cc)
  
  min_capacity = sapply(1:length(unique(cc)),function(x) min(rest_capacity[x], need_capacity[x]))
  permision = sapply(1:length(unique(cc)), function(x) c(rep(TRUE, min_capacity[x]), rep(FALSE, max(need_capacity[x]-min_capacity[x], 0)))) %>% unlist()
  
  data_public2[unique(cc), 'Current'] = data_public2[unique(cc), 'Current'] + min_capacity
  
  cr = cr[permision]
  cc = cc[permision]
  
  before_info = data.frame(index = cr, X = new_data[cr, 'X'], Y = new_data[cr, 'Y'], v = v[cr], condition = condition$condition[cr])
  before_place_info = rbind(before_place_info, before_info)
  
  d =  data_public2[cc, c('X', 'Y')]
  rownames(d) = cr
  
  new_data[cr, ] = d
  v[cr] = 0
  data_public[data_public$Class == 3,] = data_public2
  people_duration[cr,] = data.frame(place = rep(3, length(cr)), place_index = data_public2[cc, 'Index'] ,duration = rep(0, length(cr)))
  
  return(list(new_data, before_place_info, v, data_public, people_duration))
}
```

## Step 9: Get out of public areas

```{r}
outof_restaurant = function(data, data_public, people_duration, before_place_info, v, condition){
  # data: A data frame contains X and Y 
  # data_public: A data frame contains X, Y, class and condition.
  # people_duration: A data frame contains each points' place and duration
  # before_place_info: A data frame contains info of points before move to place.
  # v: A vector contains the speed of points
  # condition: A vector contains 7 factors of illness and its duration
  
  in_restaurant_index = which(people_duration$place == 3)
  possible_out_index = in_restaurant_index[people_duration[in_restaurant_index, 'duration'] > 3]
  
  num_index = length(possible_out_index)
  
  if(num_index == 0)
    return(list(data, before_place_info, v, data_public, people_duration))
  
  U = runif(num_index, 0, 1)
  confirmed_out_index = possible_out_index[U < pr]
  
  if(length(confirmed_out_index) == 0)
    return(list(data, before_place_info, v, data_public, people_duration))
  
  d = before_place_info %>% filter(index %in% confirmed_out_index) %>% arrange(index)
  
  data[confirmed_out_index,] = d[, c('X', 'Y')]
  
  v[confirmed_out_index] = d[, 'v'] * speed[condition$condition[confirmed_out_index]] / speed[d$condition]
  
  out_num = people_duration[confirmed_out_index,]$place_index %>% table()
  reduce_index = which(data_public$Index %in% names(out_num))
  data_public[reduce_index, 'Current'] = data_public[reduce_index, 'Current'] - out_num
  
  people_duration[confirmed_out_index,] = data.frame(place = 0, place_index = 0, duration = 0)
  
  before_info_delete_index = which(before_place_info$index %in% confirmed_out_index)
  before_place_info = before_place_info[-before_info_delete_index, ]
  
  return(list(data, before_place_info, v, data_public, people_duration))
}
```

## Step 10: Hospital is working!

```{r}
moveto_hospital <- function(last_data, new_data, data_public, people_duration, before_hos_info, v, condition){
  # last_data: A data frame contains X and Y which is last position
  # new_data: A data frame contains X and Y which is new position
  # data_public: A data frame contains X, Y, class and condition.
  # people_duration: A data frame contains each points' place and duration
  # before_place_info: A data frame contains info of points before move to place.
  # v: A vector contains the speed of points
  # condition: A vector contains 7 factors of illness and its duration
  
  data_public_hos = data_public %>% filter(Class == 1)
  hos_index = data_public_hos[, 'Index']
  n <- length(hos_index)
  
  N = nrow(last_data)
  moderate_index = which(condition$condition == 3 & people_duration$place != 1)
  severe_index = which(condition$condition == 4 & people_duration$place != 1)
  critical_index = which(condition$condition == 5 & people_duration$place != 1)
  movein_index = which(condition$condition %in% c(4,5) & people_duration$place != 1)
  
  n_moderate = length(moderate_index)
  n_severe = length(severe_index)
  n_critical = length(critical_index)
  n_movein = n_severe + n_critical
  
  #cat(n_moderate, n_severe, n_critical)
  empty_space = data_public_hos[,"Capacity"] - data_public_hos[,"Current"]
  vec = rep(1:length(empty_space), empty_space)
  
  if(n_movein <= sum(empty_space) & sum(data_public_hos$Capacity - data_public_hos$Current) > 0){
    if(n_movein == 0){
      return (list(new_data, data_public, people_duration, before_hos_info, v))
    }
    
    if(length(vec) == 1){
      put_in = vec[1]
    }else{
      put_in = sample(as.vector(vec),n_movein)
    }
    t1 = as.data.frame(table(put_in))
    t1 <- t1 %>% mutate(put_in = as.numeric(as.character(t1$put_in)))
    df <- data.frame(put_in = c(1:n))
    df <- left_join(df, t1, by = "put_in")
    df[is.na(df)] <- 0
    n <- df$Freq
    
    data_public_hos[,"Current"] = data_public_hos[,"Current"] + n
    
    
    #update data_public
    data_public[hos_index,] = data_public_hos
    
    #update before_hos_info
    before_info = data.frame(index = movein_index, X = new_data[movein_index, 'X'], Y = new_data[movein_index, 'Y'], v = v[movein_index], condition = condition$condition[movein_index])
    before_hos_info = rbind(before_hos_info, before_info)
    
    #update new_data
    new_data[movein_index,] = before_hos_info[before_hos_info$index %in% movein_index, c("X", "Y")]
    
    #update people_duration
    people_duration[movein_index,"place"] = 1
    people_duration[movein_index,"place_index"] = data_public_hos[put_in, 'Index']
    people_duration[movein_index,"duration"] = 0
    
    v[movein_index] = 0
  }else if(n_movein > sum(data_public_hos$Capacity - data_public_hos$Current) & sum(data_public_hos$Capacity - data_public_hos$Current) > 0){
    num_ava = sum(data_public_hos$Capacity - data_public_hos$Current)
    can_movein_index = sample(movein_index, num_ava)
    
    if(length(vec) == 1){
      put_in = vec[1]
    }else{
      put_in = sample(as.vector(vec),num_ava)
    }
    t1 = as.data.frame(table(put_in))
    t1 <- t1 %>% mutate(put_in = as.numeric(as.character(t1$put_in)))
    df <- data.frame(put_in = c(1:n))
    df <- left_join(df, t1, by = "put_in")
    df[is.na(df)] <- 0
    n <- df$Freq
    
    data_public_hos[,"Current"] = data_public_hos[,"Current"] + n
    
    #update data_public
    data_public[hos_index,] = data_public_hos
    
    #update befor_hos_info
    before_info = data.frame(index = can_movein_index, X = new_data[can_movein_index, 'X'], Y = new_data[can_movein_index, 'Y'], v = v[can_movein_index], condition = condition$condition[can_movein_index])
    before_hos_info = rbind(before_hos_info, before_info)
    
    #update new_data
    new_data[can_movein_index,] = before_hos_info[before_hos_info$index %in% can_movein_index, c("X", "Y")]
    
    #update people_duration
    people_duration[can_movein_index,"place"] = 1
    people_duration[can_movein_index,"place_index"] = data_public_hos[put_in, 'Index']
    people_duration[can_movein_index,"duration"] = 0
    
    v[can_movein_index] = 0
  }
  return (list(new_data, data_public, people_duration, before_hos_info, v))
}
```

## Step 11: Saving life

```{r}
symptom_hos_change = function(condition, people_duration){
  index4 = which(people_duration$place == 1 & condition$condition == 4)
  index5 = which(people_duration$place == 1 & condition$condition == 5)
  l4 = length(index4)
  l5 = length(index5)
  
  U4 = runif(l4, 0 ,1)
  U5 = runif(l5, 0 ,1)
  ease_index4 = index4[U4 < (transform_probability["4",1]+0.1)]
  ease_index5 = index5[U5 < (transform_probability["5",1]+0.1)]
  ease_index = c(ease_index4, ease_index5)
    
  condition[ease_index,"condition"] = condition$condition[ease_index]-1
  condition[ease_index,"duration"] = 0
    
  return(condition)
}
```

## Step 12: leave hospital

```{r}
moveout_hospital = function(last_data, new_data, data_public, people_duration, before_hos_info, v, condition){
  cure_index = sort(which(condition$condition != 3 & condition$condition != 4 & condition$condition != 5 & people_duration$place == 1))
  n_cure <- length(cure_index)
  
  if(n_cure == 0){
    return (list(new_data, data_public, people_duration, before_hos_info, v))
  }
  
  dt <- before_hos_info[before_hos_info$index %in% cure_index,]
  
  #update new_data
  new_data[cure_index,] = dt[order(dt$index), c("X", "Y")]
  
  n = table(people_duration[cure_index,"place_index"])
  hos_index = names(n)
  names(n) = NULL
  
  #update data_public
  data_public[data_public$Index %in% hos_index, 'Current'] = data_public[data_public$Index %in% hos_index, 'Current'] - n
  
  #update people_duration
  people_duration[cure_index,c("place", "place_index", "duration")] = 0
  
  #update v
  v[cure_index] = dt[order(dt$index), "v"] / speed[dt[order(dt$index), "condition"]] * speed[condition$condition[cure_index]]
  
  #update before_hos_info
  before_hos_info = before_hos_info[!before_hos_info$index %in% cure_index,]
  
  return (list(new_data, data_public, people_duration, before_hos_info, v))
}
```

## Step 13: Policy implementation

### Masks

Shiny app

### Social distancing

In step 5

### Quarantine

```{r}
start_Quarantine<-function(v,v_initial,people_duration,Quarantine_ratio,condition=condition$condition){
  
  N_all = length(v_initial)
  not_in_place_index=(1:N_all)[people_duration$place==0]
  
  N=length(not_in_place_index)
  
  quarantine_index = sample(not_in_place_index,round(Quarantine_ratio*N))
  not_quarantine_index=setdiff(not_in_place_index,quarantine_index)
  
  v[quarantine_index]=0.05 
  
  v[not_quarantine_index]=v_initial[not_quarantine_index] 

  v[not_in_place_index]=v[not_in_place_index]*speed[condition[not_in_place_index]] 
  
  return(list(v=v,last_quarantine=1))
}
```

```{r}
end_Quarantine<-function(v,v_initial,people_duration,condition=condition$condition){
  N_all = length(v_initial)
  not_in_place_index=(1:N_all)[people_duration$place==0]
  
  N = length(not_in_place_index)
  
  v[not_in_place_index] = v_initial[not_in_place_index]

  v[not_in_place_index]=v[not_in_place_index]*speed[condition[not_in_place_index]]
  return(list(v=v,last_quarantine=0))
}
```


### Close station

### Close restaurant

```{r}
close_restaurant = function(data, data_public, people_duration, before_place_info, v, condition){
  # data: A data frame containsAquamarine X and Y 
  # data_public: A data frame contains X, Y, class and condition.
  # people_duration: A data frame contains each points' place and duration
  # before_place_info: A data frame contains info of points before move to place.
  # v: A vector contains the speed of points
  # condition: A vector contains 7 factors of illness and its duration
  
  confirmed_out_index = which(people_duration$place == 3)
  if(length(confirmed_out_index) == 0)
    return(list(data, before_place_info, v, data_public, people_duration))
  
  d = before_place_info %>% filter(index %in% confirmed_out_index) %>% arrange(index)
  
  data[confirmed_out_index,] = d[, c('X', 'Y')]
  
  v[confirmed_out_index] = d[, 'v'] * speed[condition$condition[confirmed_out_index]] / speed[d$condition]
  
  out_num = people_duration[confirmed_out_index,]$place_index %>% table()
  reduce_index = which(data_public$Index %in% names(out_num))
  data_public[reduce_index, 'Current'] = data_public[reduce_index, 'Current'] - out_num
  
  people_duration[confirmed_out_index,] = data.frame(place = 0, place_index = 0, duration = 0)
  
  before_info_delete_index = which(before_place_info$index %in% confirmed_out_index)
  before_place_info = before_place_info[-before_info_delete_index, ]
  
  return(list(data, before_place_info, v, data_public, people_duration))
}
```

## Step 14: Track and quarantine close contacts

```{r}
close_contacts<-function(last_data, new_data,v,v_initial,people_duration,condition=condition$condition){
  
  N_all=length(v)
  
  
  patientnew_index=(1:N_all)[people_duration$place==1&people_duration$duration==1]
  if(patientnew_index%>%length==0){return(list(v,people_duration))}
  
  patientnew_location=last_data[patientnew_index,]
  
  not_in_place_index=(1:N_all)[people_duration$place==0]
  
  distance=pairwise_dist(patientnew_location,last_data[not_in_place_index,])
  colnames(distance)=not_in_place_index
  close_contacts_index=NULL
  for (i in seq_along(patientnew_index)){
    close_contacts_index=c(close_contacts_index,distance[i,]%>%sort()%>%head(3)%>%names)
  }

  people_duration[close_contacts_index,]$place=0.5  
  people_duration[close_contacts_index,]$duration=1
  close_contacts_index=close_contacts_index%>%as.numeric()
  v[close_contacts_index]=0
  
  
  return(list(v,people_duration))
}  
```

```{r}
close_contacts_end14<-function(last_data, new_data,v,v_initial,people_duration,condition=condition$condition){
  
  N_all=length(v_initial)
  end_of_14_index=(1:N_all)[people_duration$place==0.5&people_duration$duration==14]

  if(end_of_14_index%>%length==0){return(list(v,people_duration))}
  
  
  people_duration[end_of_14_index,]$place=0
  people_duration[end_of_14_index,]$duration=1
  v[end_of_14_index] = v_initial[end_of_14_index]

  v[end_of_14_index]=v[end_of_14_index]*speed[condition[end_of_14_index]]
  
  return(list(v,people_duration))
}  

```

```{r}
protection_ability_quarantine<-function(v,people_duration,protection_ability){
  protection_ability[protection_ability<0.05]=protection_ability[protection_ability<0.05]*21
  
  N_all=length(v)
  quarantine_index=(1:N_all)[(v==0)&(people_duration$place %in% c(0,0.5) )]
  
  if (length(quarantine_index)==0) return(protection_ability)
  
  protection_ability[quarantine_index]=protection_ability[quarantine_index]/21
  
  return(protection_ability)
  
}
```

## Step 15: Train station bring virus

```{r}
num_transfer = function(data_public, condition){
  n_capacity = data_public$Capacity[data_public$Class == 2]
  death_rate = sum(condition == 6)/length(condition)
  fear = case_when(death_rate < 0.002 ~ sample(1:round(n_capacity/5),1),
                   (death_rate>0.002 && death_rate<=0.005) ~ sample(round(n_capacity/5):round(n_capacity/5*2),1),
                   (death_rate>0.005 && death_rate<=0.01) ~ sample(round(n_capacity/5*2):round(n_capacity/5*3),1),
                   (death_rate>0.01 && death_rate<=0.03) ~ sample(round(n_capacity/5*3):n_capacity,1),
                   death_rate > 0.03 ~ sample(round(n_capacity/5*4):n_capacity,1)
  )
    n_transfer = min(round((sample(1:n_capacity,1) + fear/2)), n_capacity)
    return(n_transfer)
}
```

```{r}
movein_station = function(new_data, data_public, condition, people_duration, city, n_city){
  n_transfer = num_transfer(data_public, condition)
  can_movein_index = which(people_duration$place == 0 & condition$condition %in% c(1,2,3,7))
  if(length(can_movein_index) == 1 | n_transfer > length(can_movein_index)){
    movein_index = can_movein_index
  } else{
    movein_index = sample(can_movein_index, n_transfer)
  }
  
  new_data2 = new_data
  new_data2[movein_index, ] = data_public[data_public$Class==2, c('X', 'Y')]
  
  data_public2 = data_public
  data_public2[data_public2$Class == 2, 'Current'] = n_transfer
  
  people_duration2 = people_duration
  people_duration2[movein_index, 'place'] = 2
  people_duration2[movein_index, 'place_index'] = 1
  people_duration2[movein_index, 'duration'] = 0
  
  # # Step 17
  # if(n_city == 1 | city > n_city)
  #   stop('Wrong n_city in movein_station!')
  # 
  # dest = 1:n_city
  # dest = dest[dest != city]
  # if(n_city >= 3)
  #   travel_info = data.frame(index = movein_index, UNI = condition$UNI[movein_index], destination = sample(dest, length(movein_index), replace = TRUE))
  # if(n_city == 2)
  #   travel_info = data.frame(index = movein_index, UNI = condition$UNI[movein_index], destination = rep(dest, length(movein_index)))
  
  return(list(new_data = new_data2, #travel_info = travel_info, 
              data_public = data_public2, people_duration = people_duration2))
}
```

```{r}
visitors = function(people_duration, condition, ir1, ir2, ir3){
  index_station = which(people_duration$place == 2)
  num_station = length(index_station)
  
  U = runif(num_station, 0, 1)
  change_index1 = index_station[U < ir1]
  change_index2 = index_station[U < ir1+ir2 & U >= ir1]
  change_index3 = index_station[U < ir1+ir2+ir3 & U >= ir1+ir2]
  change_index7 = index_station[ir1+ir2+ir3 <= U]
  
  condition[change_index1, 'condition'] = 1
  condition[change_index1, 'duration'] = 0
  condition[change_index2, 'condition'] = 2
  condition[change_index2, 'duration'] = 0
  condition[change_index3, 'condition'] = 3
  condition[change_index3, 'duration'] = 0
  condition[change_index7, 'condition'] = 7
  condition[change_index7, 'duration'] = 0
  
  return(condition)
}
```


```{r}
moveout_station = function(new_data, data_public, people_duration, x_center, y_center, R){
  station_index = which(people_duration$place == 2)
  if(length(station_index) == 0)
    return(list(new_data = new_data, data_public = data_public, people_duration = people_duration))
  
  num_moveout = length(station_index)
  moveout_data = intialize_points(num_moveout, R, P, x_center, y_center)[[1]]
  
  new_data2 = new_data
  new_data2[station_index,] = moveout_data
  data_public[data_public$Class==2, 'Current'] = 0
  people_duration2 = people_duration
  people_duration2[station_index,] = data.frame(place = 0, place_index = 0, duration = 0)
  
  return(list(new_data = new_data2, data_public = data_public, people_duration = people_duration2))
  
}
```

## Step 16: More cities

```{r}
generate_center = function(R, n_city){
  x0 = c(0)
  y0 = c(0)
  max_range = 2*max(R) + 20
  min_range = 2*max(R)
  if(n_city > 1){
    while(length(x0) < n_city){
      Range = runif(1, min_range, max_range)
      Angle = runif(1, 0, 2*pi)
      X = Range * cos(Angle)
      Y = Range * sin(Angle)
      Dist = sqrt((x0 - X)^2 + (y0 - Y)^2)
      if(mean(Dist > min_range) == 1){
        x0 = c(x0, X)
        y0 = c(y0, Y)
      }
      max_range = max_range * 1.1
    }
  }
  return(list(x0 = x0, y0 = y0))
}
```

## Step 17: Travel to another city

```{r}
# assign_travel = function(travel_info, n_city){
#   travelin_info = list()
#   for(i in 1:n_city)
#     travelin_info[[i]] = data.frame(NULL)
#   
#   for(i in 1:n_city){ # out
#     for(j in 1:n_city){ # in
#       travelin_info[[j]] = rbind(travelin_info[[j]], travel_info[[i]][travel_info[[i]]$destination == j, c('UNI', 'destination')])
#     }
#   }
#   return(travelin_info = travelin_info)
# }
```

```{r}
# travel_data_change = function(travel_info, n_city, new_data, data_public, condition, v, infectious_ability, protection_ability, people_duration, v_initial){
#   
#   travelin_info = assign_travel(travel_info, n_city)
#   
#   Travel_new_data = data.frame(NULL)
#   Travel_condition = data.frame(NULL)
#   Travel_v = data.frame(NULL)
#   Travel_infectious_ability = data.frame(NULL)
#   Travel_protection_ability = data.frame(NULL)
#   Travel_v_initial = data.frame(NULL)
#   Travel_people_duration = data.frame(NULL)
#   
#   new_data2 = new_data
#   condition2 = condition
#   v2 = v
#   infectious_ability2 = infectious_ability
#   protection_ability2 = protection_ability
#   v_initial2 = v_initial
#   people_duration2 = people_duration
#   
#   for(i in 1:n_city){ # record out and delete
#     Travel_new_data = rbind(Travel_new_data, cbind(UNI = travel_info[[i]]$UNI,  new_data2[[i]][travel_info[[i]]$index, ]))
#     new_data2[[i]] = new_data2[[i]][-travel_info[[i]]$index,]
#     Travel_condition = rbind(Travel_condition, cbind(UNI = travel_info[[i]]$UNI, condition2[[i]][travel_info[[i]]$index, ]))
#     condition2[[i]] = condition2[[i]][-travel_info[[i]]$index,]
#     Travel_people_duration = rbind(Travel_people_duration, cbind(UNI = travel_info[[i]]$UNI, people_duration2[[i]][travel_info[[i]]$index, ]))
#     people_duration2[[i]] = people_duration2[[i]][-travel_info[[i]]$index,]
#     
#     Travel_v = rbind(Travel_v, cbind(UNI = travel_info[[i]]$UNI, v2[[i]][travel_info[[i]]$index]))
#     v2[[i]] = v2[[i]][-travel_info[[i]]$index]
#     Travel_infectious_ability = rbind(Travel_infectious_ability, cbind(UNI = travel_info[[i]]$UNI, infectious_ability2[[i]][travel_info[[i]]$index]))
#     infectious_ability2[[i]] = infectious_ability2[[i]][-travel_info[[i]]$index]
#     Travel_protection_ability = rbind(Travel_protection_ability, cbind(UNI = travel_info[[i]]$UNI, protection_ability2[[i]][travel_info[[i]]$index]))
#     protection_ability2[[i]] = protection_ability2[[i]][-travel_info[[i]]$index]
#     Travel_v_initial = rbind(Travel_v_initial, cbind(UNI = travel_info[[i]]$UNI, v_initial2[[i]][travel_info[[i]]$index]))
#     v_initial2[[i]] = v_initial2[[i]][-travel_info[[i]]$index]
#     
#   }
#   
#   for(i in 1:n_city){ # data in
#     N0 = sum(Travel_condition$UNI %in% travelin_info[[i]]$UNI)
#     new_data2[[i]] = rbind(new_data2[[i]], data.frame(X = rep(data_public[[i]][data_public[[i]]$Class == 2, 'X'], N0), Y = rep(data_public[[i]][data_public[[i]]$Class == 2, 'Y'], N0)))
#     rownames(new_data2[[i]]) = 1:nrow(new_data2[[i]])
#     condition2[[i]] = rbind(condition2[[i]], Travel_condition[Travel_condition$UNI %in% travelin_info[[i]]$UNI, -1])
#     rownames(condition2[[i]]) = 1:nrow(condition2[[i]])
#     people_duration2[[i]] = rbind(people_duration2[[i]], Travel_people_duration[Travel_people_duration$UNI %in% travelin_info[[i]]$UNI, -1])
#     rownames(people_duration2[[i]]) = 1:nrow(people_duration2[[i]])
#     
#     v2[[i]] = c(v2[[i]], Travel_v[Travel_v$UNI %in% travelin_info[[i]]$UNI, -1])
#     infectious_ability2[[i]] = c(infectious_ability2[[i]], Travel_infectious_ability[Travel_infectious_ability$UNI %in% travelin_info[[i]]$UNI, -1])
#     protection_ability2[[i]] = c(protection_ability2[[i]], Travel_protection_ability[Travel_protection_ability$UNI %in% travelin_info[[i]]$UNI, -1])
#     v_initial2[[i]] = c(v_initial2[[i]], Travel_v_initial[Travel_v_initial$UNI %in% travelin_info[[i]]$UNI, -1])
#     
#   }
#   
#   Traveler = Travel_new_data$UNI
#   
#   return(list(new_data = new_data2, condition = condition2, v = v2, infectious_ability = infectious_ability2, protection_ability = protection_ability2, v_initial = v_initial2, people_duration = people_duration2, Traveler = Traveler))
# }
```

## Step 18: Recrudesce

```{r}
recrudesce<-function(condition, vaccine){
  cured<-which(condition$condition == 7 & condition$duration > 7)
  l<-length(cured)
  
  if(l==0 | vaccine){
    return(condition)
  }
  else{
    condition.recrudesce<-sample(c(1, 3:5, 7), l , replace = T, prob = c(0.015, 0.003, 0.001, 0.001, 0.98))
    condition$condition[cured]<-condition.recrudesce
    index<-which(condition.recrudesce != 7)
    condition$duration[cured[index]]<-0
    
    return(condition)
  }
}
```

## Step 19: Vaccine

```{r}
vaccine<-function(condition, protection_ability){
  index<-which(condition$condition %in% c(1,2) & protection_ability>0)
  n<-length(index)
  
  if(n==0){
    return(protection_ability)
  }
  
  else{
    vaccine<-sample(0:1,n, replace = T, prob=c(0.7, 0.3))
    protection_ability[index[vaccine == 1]]<-0.05
    
    return(protection_ability)
  }
}
```

## Step 20: Simulation

```{r}
simulation_points = function(N, R, P, Num_public, Times, n_city){
  # N: Total number of points
  # R: A vector of radius
  # P: A vector of the proportion of points in each ring area
  # Time: The number of days (running times)
  
  Start_time = Sys.time()
  
  whole_data = data.frame(X = NULL, Y = NULL, Condition = NULL, Time = NULL, City = NULL)
  centers = generate_center(R, n_city)
  
  if(n_city == 1){
    NN = N
    Num_publicN = Num_public
  }
  RN = list()
  RN[[1]] = R
  if(n_city > 1){
    NN = c(N, round(runif(n_city-1, 0.3, 0.6)*N))
    Num_publicN = c(Num_public, round(runif(n_city-1, 0.4, 0.6)*Num_public))
    for(i in 2:n_city){
      RN[[i]] = runif(1, 0.6, 0.8)*R
    }
  }
  
  
  data = list()
  condition = list()
  v = list()
  infectious_ability = list()
  protection_ability = list()
  data_public = list()
  people_duration = list()
  before_place_info = list()
  before_hos_info = list()
  v_initial = list()
  new_data = list()
  travel_info = list()
  
  for(i in 1:n_city){
    # Step 1
    intialize = intialize_points(NN[i], RN[[i]], P, centers$x0[i], centers$y0[i])
    data[[i]] = intialize[[1]]
    # Step 5
    condition[[i]] = data.frame(condition = rep(1, NN[i]), duration = rep(0, NN[i]))
    # condition[[i]] = data.frame(condition = rep(1, NN[i]), duration = rep(0, NN[i]), UNI = (cumsum(NN)-NN+1)[i]:(cumsum(NN))[i])
    whole_data = rbind(whole_data, cbind(data[[i]], Condition = condition[[i]]$condition, Time = rep(0, NN[i]), City = rep(i, NN[i])))
    # Step 3
    v2 = rnorm(NN[i], 2, 0.8)
    v2[v2 < 0.1] = 0.1
    v[[i]] = v2
    # Step 5
    infectious_ability[[i]] = rep(1, NN[i])
    protection_ability2 = rnorm(NN[i], 1, 0.3)
    protection_ability2[protection_ability2 < 0.05] = 0.05
    protection_ability2[protection_ability2 > 1] = 1
    protection_ability[[i]] = protection_ability2
    # Step 7
    data_public[[i]] = intialize_public_place(RN[[i]], P, NN[i], Num_publicN[i], Hospital_capacity, centers$x0[i], centers$y0[i])
    # Step 8
    people_duration[[i]] = data.frame(place = rep(0, NN[i]), place_index = rep(0, NN[i]), duration = rep(0, NN[i]))
    before_place_info[[i]] = data.frame(index = NULL, X = NULL, Y = NULL, v = NULL, condition = NULL)
    # Step 10
    before_hos_info[[i]] = data.frame(index = NULL, X = NULL, Y = NULL, v = NULL, condition = NULL)
    # Step 13
    v_initial[[i]] = v[[i]] 
    # Step 15
    # travel_info[[i]] = data.frame(index = NULL, UNI = NULL, destination = NULL)
  }
  # Step 5
  condition[[1]] = initialize_infector(condition[[1]], 5)

  # Step 13
  # Close restaurant
  trigger_restaurant = TRUE 
  # Social distance
  trigger_social_distance = FALSE
  # Quarantine
  trigger_quarantine = FALSE 
  last_quarantine = 0
  # Step 19
  vacday = 0
  
  # If change nrow of data, need to change nrow of condition
  for(t in 1:Times){
    if(t == 15)
      trigger_social_distance = TRUE
    if(t == 25)
      trigger_restaurant = FALSE
    if(t == 15)
      trigger_quarantine = TRUE
    if(t == 35)
      trigger_quarantine = FALSE
    if(t > 20)
      vacday = vacday + 1
    
    ir1 = 0
    ir2 = 0
    ir3 = 0
    for(i in 1:n_city){
      ir1 = ir1 + sum(condition[[i]]$condition == 1)
      ir2 = ir2 + sum(condition[[i]]$condition == 2)
      ir3 = ir3 + sum(condition[[i]]$condition == 3)
    }
    ir1 = ir1/sum(NN)
    ir2 = ir2/sum(NN)
    ir3 = ir3/sum(NN)
    
    for(i in 1:n_city){
      condition[[i]]$duration = condition[[i]]$duration + 1
      people_duration[[i]]$duration = people_duration[[i]]$duration + 1
      # Step 3
      new_data[[i]] = random_walk(data[[i]], v[[i]])
      # Step 4
      new_data[[i]] = through_wall(data[[i]], new_data[[i]], RN[[i]], alpha, centers$x0[i], centers$y0[i])
      # Step 5
      condition[[i]] = infection(new_data[[i]], v[[i]], condition[[i]], infectious_ability[[i]], protection_ability[[i]], pc, trigger_social_distance, social_distance)
      # Step 6
      temp = condition_change(condition[[i]], v[[i]], transform_probability, speed)
      condition[[i]] = temp[[1]]
      v[[i]] = temp[[2]]
      
      # Step 15
      temp = moveout_station(new_data[[i]], data_public[[i]], people_duration[[i]], centers$x0[i], centers$y0[i], RN[[i]])
      new_data[[i]] = temp[[1]]
      data_public[[i]] = temp[[2]]
      people_duration[[i]] = temp[[3]]

      condition[[i]] = visitors(people_duration[[i]], condition[[i]], ir1, ir2, ir3)
      
      temp = movein_station(new_data[[i]], data_public[[i]], condition[[i]], people_duration[[i]], city = i, n_city)
      new_data[[i]] = temp[[1]]
      #travel_info[[i]] = temp[[2]]
      data_public[[i]] = temp[[2]]
      people_duration[[i]] = temp[[3]]
      
      # Step 8
      if(trigger_restaurant == TRUE){
        temp = moveto_restaurant(data[[i]], new_data[[i]], data_public[[i]], people_duration[[i]], before_place_info[[i]], v[[i]], condition[[i]])
        new_data[[i]] = temp[[1]]
        before_place_info[[i]] = temp[[2]]
        v[[i]] = temp[[3]] 
        data_public[[i]] = temp[[4]]
        people_duration[[i]] = temp[[5]]
      }
      # Step 9
      if(trigger_restaurant == TRUE){#Step 13
        temp = outof_restaurant(new_data[[i]], data_public[[i]], people_duration[[i]], before_place_info[[i]], v[[i]], condition[[i]])
      } else{
        temp = close_restaurant(new_data[[i]], data_public[[i]], people_duration[[i]], before_place_info[[i]], v[[i]], condition[[i]])
      }
      new_data[[i]] = temp[[1]]
      before_place_info[[i]] = temp[[2]]
      v[[i]] = temp[[3]] 
      data_public[[i]] = temp[[4]]
      people_duration[[i]] = temp[[5]]
      # Step 10
      temp = moveto_hospital(data[[i]], new_data[[i]], data_public[[i]], people_duration[[i]], before_hos_info[[i]], v[[i]], condition[[i]])
      new_data[[i]] = temp[[1]]
      before_hos_info[[i]] = temp[[4]]
      v[[i]] = temp[[5]]
      data_public[[i]] = temp[[2]]
      people_duration[[i]] = temp[[3]]
      # Step 11
      condition[[i]] = symptom_hos_change(condition[[i]], people_duration[[i]])
      # Step 12
      temp = moveout_hospital(data[[i]], new_data[[i]], data_public[[i]], people_duration[[i]], before_hos_info[[i]], v[[i]], condition[[i]])
      new_data[[i]] = temp[[1]]
      before_hos_info[[i]] = temp[[4]]
      v[[i]] = temp[[5]]
      data_public[[i]] = temp[[2]]
      people_duration[[i]] = temp[[3]]
      # Step 13
      ## Quarantine
      if(trigger_quarantine==T){
        temp = start_Quarantine(v[[i]], v_initial[[i]], people_duration[[i]], Quarantine_ratio = Quarantine_ratio, condition = condition[[i]]$condition)
        v[[i]] = temp[[1]]
        last_quarantine = temp[[2]]
      }
      if(trigger_quarantine == F & last_quarantine == 1){
        temp = end_Quarantine(v[[i]], v_initial[[i]], people_duration[[i]], condition = condition[[i]]$condition)
        v[[i]] = temp[[1]]
        last_quarantine = temp[[2]]
      }
      # Step 14
      temp = close_contacts(data[[i]], new_data[[i]], v[[i]], v_initial[[i]], people_duration[[i]], condition = condition[[i]]$condition)
      v[[i]] = temp[[1]]
      people_duration[[i]] = temp[[2]]
      temp=close_contacts_end14(data[[i]], new_data[[i]], v[[i]], v_initial[[i]], people_duration[[i]], condition = condition[[i]]$condition)
      v[[i]] = temp[[1]]
      people_duration[[i]] = temp[[2]]
      protection_ability[[i]] = protection_ability_quarantine(v[[i]], people_duration[[i]], protection_ability[[i]])
      
      
      
      # Step 18
      condition[[i]] = recrudesce(condition[[i]], vacday > vacstart)
      # Step 19
      if(vacday > vacstart)
        protection_ability[[i]] = vaccine(condition[[i]], protection_ability[[i]])

      
      
      whole_data = rbind(whole_data, cbind(new_data[[i]], Condition = condition[[i]]$condition, Time = rep(t, nrow(new_data[[i]])), City = rep(i, nrow(new_data[[i]]))))
      data[[i]] = new_data[[i]]
    }

  }
  
  End_time = Sys.time()
  
  for(i in 1:n_city){
    check_data = data[[i]] %>% mutate(Radiu = sqrt((X-centers$x0[i])^2 + (Y-centers$y0[i])^2))
    c1 = check_data %>% filter(Radiu<RN[[i]][1]) %>% nrow()
    c2 = check_data %>% filter(Radiu<RN[[i]][2]) %>% nrow()
    c3 = check_data %>% filter(Radiu<RN[[i]][3]) %>% nrow()
    c4 = check_data %>% filter(Radiu<RN[[i]][4]) %>% nrow()
    cat('Running times:',t, 'Population:', c1, c2, c3, c4, '\n')
  }
  cat('Used time: ')
  print(End_time-Start_time)
  cat('\n')
  
  return(list(whole_data, data_public))
}
```

```{r}
temp= simulation_points(N, R, P, Num_public, Times, n_city)
whole_data = temp[[1]]
data_public_temp = temp[[2]]
data_public = data.frame(NULL)
for(i in 1:n_city){
  data_public = rbind(data_public, data_public_temp[[i]])
}
```

## Step 21: Generate gganimate gif

```{r}
generate_gif = function(whole_data, data_public){
  # whole_data: A data.frame contains X, Y, Condition and Time
  # data_public: A data frame contains X, Y, class and condition.
  
  data_public$Class = factor(data_public$Class, levels = 1:4, labels = c('Hospital', 'Station', 'Restaurant', 'Hotel'))
  
  p = whole_data %>% 
    ggplot(aes(x = X, y = Y, color = factor(Condition, levels = 1:7), group = 1L)) + 
    geom_point(size = 0.1, alpha = 0.6) + 
    geom_point(data = data_public, aes(x = X, y = Y, size = log(Capacity), color = Class), alpha = 0.8) + 
    scale_color_manual(values = c('1' = '#00CC00', '2' = '#FFCC00', '3' = '#FF69B4', '4' = '#DC143C', '5' = '#8B0000', '6' = '#000000', '7' = '#00CCFF', 'Hospital' = '#FF0000', 'Station' = '#FF6600', 'Restaurant' = '#7FFFD4', 'Hotel' = '#CC99CC'), labels = c('Healthy', 'Incubation', 'Moderate', 'Severe', 'Cirtical', 'Death', 'Cure', 'Hospital', 'Station', 'Restaurant', 'Hotel'), name = 'Condition') +
    scale_size(range = c(1,2.5), name = 'Capacity', guide = FALSE) + 
    coord_fixed() + 
    transition_time(Time) + 
    ease_aes('linear') + 
    my_theme
  
  image <- animate(p, fps = 10, nframes = Times * 4)
  image_write(image, "output.gif")
}

```

```{r}
generate_gif(whole_data, data_public)
```





